Interfering with Noninterference \iftext\thanks{\bcp{Identify applicable funding agencies here (DARPA and NSF and...?)}}\fi

### 2020-01-12 main.tex
Thoughts

@@

\bcp{
  Following is not quite right.  Better intuition:
  \begin{itemize}
  \item A (micro-){\em policy} is a function that takes a contour to
  \begin{enumerate}
  \item a private type $X$
  \item an initial value of $X$
  \item a partial step function of type $(\MACHS,X) \rightharpoonup
  (\MACHS,X)$ that, when defined, agrees with $\stepstounderfull$ on
  machine states.
  \end{enumerate}
  That is, it takes a starting contour and produces a runtime monitor, which
  carries along some information that it uses to decide when to terminate
  execution early.
  \item A {\em property} is a function that takes a contour to a
  prefix-closed set of (finite and/or infinite) sequences of machine states.
  That is, it takes a starting contour and produces a checker that tells
  whether a given trace is OK to observe.
  \item A policy $p$ {\em guarantees} a property $P$ if, for each contour
  $\contour$, the sequence of machine states obtained by projecting the
  sequence of ..... ARGH WHAT ABOUT VARIANTS!?!
  \item Proposal: Forget about full-blown NI and make the whole paper be
  about ``lockstep NI'' where the PC is the same in every pair of
  related runs
  \begin{itemize}
  \item One issue that I am not sure about: Could there be a sneaky way of
  ``putting secret information into the control state'' where the PCs of
  related runs are always in lockstep but, because the instruction memory is
  writeable, different instructions can get dispatched.  E.g., XXXX
  \item So maybe we should be asking that the instruction stream be
  identical, not (just?) the PCs
  \item One nice observation is that, if we are only interested in pairs of
  runs with identical PCs, there are two different ways to proceed: (1) say
  that we {\em ignore} runs where the PCs (or instruction streams) diverge
  (e.g., taint tracking), or (2) {\em disallow} runs where the PCs (or
  instruction streams) diverge, i.e., demand that this never happens (e.g.,
  stack and heap policies).
  \end{itemize}
  \item A remaining question is what to do about the possibility that the
  contour changes differently on two related runs.  We could disallow this,
  but not certain it's necessary---maybe everything works out OK.
  \end{itemize}
}

Formally, a {\em policy}
$\pol \in (\CONTOURS \times \MACHS) \rightarrow (\CONTOURS \times
\MACHS)$ is an enriched
step function that works on pairs of contours and machines---i.e., it is a
partial function taking a contour and a machine state to an updated contour
and machine state that, wherever is is defined, agrees with
$\stepstounderfull$.  That is,
it represents an enforcement mechanism that sometimes halts programs earlier
than the bare step relation does, but that agrees with the bare step
relation when it allows evaluation to proceed.  We write
$(\contour_1,\mach_1) \stepstounder{\pol} (\contour_2,\mach_2)$ for
$\pol(\contour_1,\mach_1) = (\contour_2,\mach_2)$.

>>>>

Informally, a (micro-){\em policy}
is an enriched
step function that works on pairs of contours and machines---i.e., it is a
partial function taking a contour and a machine state to an updated contour
and machine state that, wherever is is defined, agrees with
$\stepstounderfull$.  That is,
it represents an enforcement mechanism that sometimes halts programs earlier
than the bare step relation does, but that agrees with the bare step
relation when it allows evaluation to proceed.  We write
$(\contour_1,\mach_1) \stepstounder{\pol} (\contour_2,\mach_2)$ for
$\pol(\contour_1,\mach_1) = (\contour_2,\mach_2)$.

Formally, a policy
%
$\pol \in \CONTOURS \rightarrow \exists X.\; X \times (\MACHS \times X
\rightharpoonup \MACHS \times X)$
%
 is a function that takes a contour to
\begin{enumerate*}
  \item a private type $X$,
  \item an initial value of $X$, and
  \item a partial step function of type
  $(\MACHS \times X) \rightharpoonup (\MACHS \times X)$ that, when defined,
  agrees with $\stepstounderfull$ on machine states.
\end{enumerate*}
That is, a policy takes a starting contour and produces a runtime monitor
that carries along some private information and uses it to decide whether to
terminate execution early.

@@

\bcp{
  \begin{itemize}
  \item A {\em property} is a function that takes a contour to a
  prefix-closed set of (finite and/or infinite) sequences of machine states.
  That is, it takes a starting contour and produces a checker that tells
  whether a given trace is OK to observe.
  \item A policy $p$ {\em guarantees} a property $P$ if, for each contour
  $\contour$, the sequence of machine states obtained by projecting the
  sequence of ..... ARGH WHAT ABOUT VARIANTS!?!
  \item Proposal: Forget about full-blown NI and make the whole paper be
  about ``lockstep NI'' where the PC is the same in every pair of
  related runs
  \begin{itemize}
  \item One issue that I am not sure about: Could there be a sneaky way of
  ``putting secret information into the control state'' where the PCs of
  related runs are always in lockstep but, because the instruction memory is
  writeable, different instructions can get dispatched.  E.g., XXXX
  \item So maybe we should be asking that the instruction stream be
  identical, not (just?) the PCs
  \item One nice observation is that, if we are only interested in pairs of
  runs with identical PCs, there are two different ways to proceed: (1) say
  that we {\em ignore} runs where the PCs (or instruction streams) diverge
  (e.g., taint tracking), or (2) {\em disallow} runs where the PCs (or
  instruction streams) diverge, i.e., demand that this never happens (e.g.,
  stack and heap policies).
  \end{itemize}
  \item A remaining question is what to do about the possibility that the
  contour changes differently on two related runs.  We could disallow this,
  but not certain it's necessary---maybe everything works out OK.
  \end{itemize}
}
